Radio Properties of Young Protostars in the Central Filament of the Serpens South Infrared Dark Cloud

### 2014-12-27 Paper/paper.tex
new file:   AAS_2015/SS_AAS_Poster.ai 	new file:   AAS_2015/SS_AAS_Poster.pdf 	modified:   Make_Figs.py 	modified:   Paper/figures/Shirley36_Correlation-eps-converted-to.pdf 	modified:   Paper/figures/Shirley60_Correlation-eps-converted-to.pdf 	modified:   Paper/figures/Spix_Class-eps-converted-to.pdf 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib 	modified:   Radio_Correlations.py 	modified:   SERPS_SED.py 	modified:   git_add.sh

VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 3	&	50	&	60 $\pm$ 3	&	44	&	-0.22 $\pm$ 0.07	&	-0.31 $\pm$ 0.3	&	Class 0$^{*}$?\\[1ex]

@@

VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 6	&	36	&	73 $\pm$ 5	&	58	&	1.5 $\pm$ 0.17	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]

@@

VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 4	&	37	&	83 $\pm$ 4	&	61	&	2.29 $\pm$ 0.15	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]

@@

VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 8	&	135	&	161 $\pm$ 9	&	167	&	0.22 $\pm$ 0.08	&	0.5 $\pm$ 0.12	&	Class I\\[1ex]

@@

\begin{figure*}
\label{fig:vla4}
\centering
\includegraphics[keepaspectratio=True,scale=.7]{figures/SerpSouth_VLA4_contour.eps}
\caption{\small{ 
}}
\end{figure*}

@@

@@

-- Given the size of the beam and the size of VLA 1 and 4, should they be considered ``resolved'' ? \\

@@

>>>>

VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 3	&	50	&	60 $\pm$ 3	&	44	&	-0.22 $\pm$ 0.07	&	-0.31 $\pm$ 0.3	&	Class 0?\\[1ex]

@@

VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 6	&	36	&	73 $\pm$ 5	&	58	&	1.5 $\pm$ 0.17	&	1.14 $\pm$ 0.34	&	Class 0,VeLLO\\[1ex]

@@

VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 4	&	37	&	83 $\pm$ 4	&	61	&	2.29 $\pm$ 0.15	&	1.19 $\pm$ 0.33	&	Class 0\\[1ex]

@@

VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 8	&	135	&	161 $\pm$ 9	&	167	&	0.22 $\pm$ 0.08	&	0.5 $\pm$ 0.12	&	Class I,VeLLO\\[1ex]

@@

@@

\citep{Dunham13}

@@

-- Given the size of the beam size compared to the size of VLA 1 and 4, should they be considered ``resolved'' ? \\

@@

\begin{figure}
\label{fig:vla4}
\centering
\includegraphics[keepaspectratio=True,scale=.6]{figures/SerpSouth_VLA4_contour.eps}
\caption{\small{ Zoom-in on sources VLA 2, 3 and 4. Blue solid and red dashed contours correspond to 4.1 and 6.3 cm images respectively. Radio contours start at their respective 3$\sigma$ levels.
}}
\end{figure}
